Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-29 manuscript.Rmd
recode 99 into NA

# rename variables for a final time
ids <- paste(c("perceiver", "target", "dyad", "group"), "id", sep = "_")
rapport <- paste0("rapport", 1:16)
personality <- map(c("perceiver_trait", "target_trait", "judgment_trait"),
                   ~ paste0(.x, 1:26)) |> unlist()
affect <- map(c("perceiver_affect", "target_affect", "judgment_affect"),
              ~ paste0(.x, 1:120)) |> unlist()
sbw <- paste0("swb", 1:5)
informant <- paste0("informant_trait", 1:26)

@@

## Descriptive statistics
```{r, include = FALSE}
descriptive_df <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
  )

@@

```{r}
# Peer Review: Perhaps you can use a package like the "gt" package to format the table 
table1
```

@@

sjPlot::tab_model(normEASRM, diffEASRM)

#PEER REVIEW: I notice you are writing very similar models across different outcomes, is there an option to create a function and reduce some of the repetitive code?
```

@@

#PEER REVIEW: Random note, I used to work with Dr. Karyn Lewis when she was at Education Northwes :)

>>>>

# rename variables for a final time
ids <- paste(c("perceiver", "target", "dyad", "group"), "id", sep = "_")
rapport <- paste0("rapport", 1:16)
personality <- map(c("perceiver_trait", "target_trait", "judgment_trait"),
                   ~ paste0(.x, 1:26)) %>% unlist()
affect <- map(c("perceiver_affect", "target_affect", "judgment_affect"),
              ~ paste0(.x, 1:120)) %>% unlist()
sbw <- paste0("swb", 1:5)
informant <- paste0("informant_trait", 1:26)

@@

# recode 99s into NA
recode_99s <- 
psych::describe(df[-9]) %>% 
  rownames_to_column() %>% 
  filter(max == 99) %>% 
  select(rowname)

df2 <-  
df %>% 
  mutate(
    across(recode_99s$rowname, ~ na_if(.x, 99))
  )
```

## Descriptive statistics
```{r, include = FALSE}
# descriptives
descriptive_df <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
  )

@@

```{r}
table1
```

@@

sjPlot::tab_model(normEASRM, diffEASRM)
```

@@
